---
title: "ADH 2019 replication"
author: "Michael Keller and Benedikt Marxer"
date: "4 4 2022"
output:
  html_document:
    toc: true
    number_sections: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
here::i_am("ADH 2019 replication.Rmd")
library(here)
library(tidyverse)
library(haven)
```

# About ADH 2019

When Work Disappears: Manufacturing Decline and the Falling Marriage Market Value of Young Men.AER: Insights 2019, 1(2): 161–178. DOI: https://doi.org/10.1257/aeri.20180010

# Setup

Download the replication files: https://www.openicpsr.org/openicpsr/project/116320/version/V1/view?path=/openicpsr/116320/fcr:versions/V1&type=project
Make sure to unzip the files and move the top folder (*"116320-V1"*) to the top level of this repository (blocked in the .gitignore). 


# Load data


```{r loaddata}
workfile9014wwd <- read_dta(here::here("116320-V1", "ADH-WWD-AERi-Data", "dta", "workfile9014wwd.dta"))
czone9014_percentiles <- read_dta(here::here("116320-V1", "ADH-WWD-AERi-Data", "dta", "czone9014_percentiles.dta"))
```

## Equation (1)

Equation (1): $$\Delta IP_{i \tau}^{cu} = \sum_j \frac{L_{ij90}}{L_{i90}} \Delta IP_{j \tau}^{cu} $$

Where $\Delta IP_{j \tau}^{cu} = \Delta M_{j \tau}^{cu} / (Y_{j91} + M_{j91 - X_{j91}})$ is the growth of Chinese import penetration in the US for industry $j$ over period $\tau$, which in the authors' data inlude the time intervals 1990 to 2000 and 2000 to 2014.


