---
title: "ADH 2019 replication"
author: "Michael Keller and Benedikt Marxer"
date: "4 4 2022"
output:
  html_document:
    toc: true
    number_sections: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
here::i_am("ADH 2019 replication.Rmd")
library(here)
library(tidyverse)
library(haven)
```

# About ADH 2019

When Work Disappears: Manufacturing Decline and the Falling Marriage Market Value of Young Men. AER: Insights 2019, 1(2): 161–178. DOI: https://doi.org/10.1257/aeri.20180010

# Setup

Download the replication files: https://www.openicpsr.org/openicpsr/project/116320/version/V1/view?path=/openicpsr/116320/fcr:versions/V1&type=project
Make sure to unzip the files and move the top folder (*"116320-V1"*) to the top level of this repository (blocked in the .gitignore). 


# Load data


```{r loaddata}
workfile9014wwd <- read_dta(here::here("116320-V1", "ADH-WWD-AERi-Data", "dta", "workfile9014wwd.dta"))
czone9014_percentiles <- read_dta(here::here("116320-V1", "ADH-WWD-AERi-Data", "dta", "czone9014_percentiles.dta"))
```


## About the data: {.tabset}

### First data set: workﬁle9014wwd.dta

Provides data for 722 Commuting Zones (CZs) times 2 time periods (1990-2000,2000-2014). This ﬁle is the basis for all tabulated regression results. 


```{r overviewd1, eval=FALSE}
# library(summarytools)
# dfSummary(workfile9014wwd$czone)
workfile9014wwd$czone # iIdentifies Community Zone (722)
workfile9014wwd$statefip # indicates the State that comprises most of the CZs population

workfile9014wwd$yr # identifies the time period (1990-2000, 2000-2014)
workfile9014wwd$t2 # also identifies the time periods (1 and 2)

workfile9014wwd$reg_midatl # identifies the Census division of the CZ (8 divisions)

workfile9014wwd$timepwt24 # weight variable, indicates each CZ’s share in the start-of-period population of the 48 U.S. mainland states, multiplied by 1/10 of the period length (10 or 14 years).

workfile9014wwd$d_impusch_p9 captures # captures a CZ’s exposure to growing import penetration from China
workfile9014wwd$d_impuschm_p9cen  # male component
workfile9014wwd$d_impuschf_p9cen # female component

# The variables d_impotch*_p9cen_lag denote the corresponding instruments using other developed countries’ imports from China. All other variables with preﬁx “d_” are outcome variables of the regression analysis and are measured as 10-year equivalent changes. All variables with preﬁx “l_” are start-of-period values that are used either for descriptive statistics or as control variables. Finally, variables starting with “cum_mort” measure cumulate per-decade mortality.

```

### Second data set: czone9014_percentiles.dta

Provides additional data 

```{r overviewd2, , eval=FALSE}
# contains the initial levels and subsequent changes of all percentiles of the gender-speciﬁc distributions of annual wage and salary earnings in a CZ. 
czone9014_percentiles$czone
czone9014_percentiles$yr

czone9014_percentiles$l_inc1839m_p1 # income males percentile 1 (All variables with preﬁx “l_” are start-of-period values that are used either for descriptive statistics or as control variables.)
czone9014_percentiles$l_inc1839f_p1 # income females percentile 1

czone9014_percentiles$d_inc1839m_p1 # income males percentile 1 (All variables with preﬁx “d_” are outcome variables of the regression analysis and are measured as 10-year equivalent changes.)
czone9014_percentiles$d_inc1839f_p1 # income females percentile 1


```


## Equation (1)

Equation (1): $$\Delta IP_{i \tau}^{cu} = \sum_j \frac{L_{ij90}}{L_{i90}} \Delta IP_{j \tau}^{cu} $$

Where $\Delta IP_{j \tau}^{cu} = \Delta M_{j \tau}^{cu} / (Y_{j91} + M_{j91 - X_{j91}})$ is the growth of Chinese import penetration in the US for industry $j$ over period $\tau$, which in the authors' data inlude the time intervals 1990 to 2000 and 2000 to 2014.


