---
title: "ADH 2019 Replication"
author: 
- Michael Keller
- Benedikt Marxer
date: "25 4 2022"
output:
  html_document:
    toc: true
    number_sections: true
    toc_float: true
---
# About ADH 2019

Autor, David, David Dorn, and Gordon Hanson. 2019. "When Work Disappears: Manufacturing Decline and the Falling Marriage Market Value of Young Men." *American Economic Review: Insights*, 1 (2): 161-78. DOI: https://doi.org/10.1257/aeri.20180010

# Setup

Before running, install the bartik.weight package (Source: https://github.com/paulgp/bartik-weight/tree/master/R-code):

```{r bartik-package, eval=F, echo=TRUE}
# install.packages("devtools")
devtools::install_github("paulgp/bartik-weight/R-code/pkg")
```

Load all relevant packages:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(haven)
library(bartik.weight)
library(AER)
library(stargazer)
```

```{r setup-visible,  eval=F, echo=T}
library(tidyverse)
library(haven)
library(bartik.weight)
library(AER)
library(stargazer)
```

Load all the data files that are needed for the replication. The data frames are named following the Bartik package nomenclature.

```{r import-data}
## Main data set
# Source: https://www.ddorn.net/data
temp <- tempfile()
download.file("https://www.ddorn.net/data/ADH-WWD-FileArchive.zip", temp, mode = "wb")
master <- read_dta(unz(temp, "ADH-WWD-AERi-Data/dta/workfile9014wwd.dta"))
unlink(temp)

## ADH China Shock: "Global" Industry-level Growth of Imports (year-industry level)
# Source: https://github.com/paulgp/bartik-weight
ADH_global <- bartik.weight::ADH_global

## ADH China Shock: Local Industry Shares (community-year-industry level)
# Source: https://github.com/paulgp/bartik-weight
ADH_local <- bartik.weight::ADH_local
```


# IV Approach {.tabset}

1st stage: $x = a_0 + a_1*B + n$,  with $B=z*g$  
2nd stage: $y = b_0 + b_1*x + e$

$x$ = Change in import exposure -> `master$d_impusch_p9` (endogen)   
$y$ = change manufacturing employment -> `master$d_sh_empl_mfg_age1839` (outcome)  
$z$ = Chinese export growth -> `master$d_impotch_p9_lag` (instrument for endogenous x) 

## Effect on Employment Status

Estimated Impact of Manufacturing Trade Shock on Manufacturing Employment by Gender and Gender Differential in Employment Status, Earnings, and Idleness, 1990–2014

*I. Overall trade shock* 

**M+F**
```{r}
mainshock_mf <- ivreg(formula = d_sh_empl_mfg_age1839 ~ d_impusch_p9 + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic | d_impotch_p9_lag + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic, weights = timepwt24, data=master)
```

**M**

```{r}
mainshock_m <- ivreg(formula = d_sh_empl_mfg_age1839m ~ d_impusch_p9 + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic | d_impotch_p9_lag + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic, weights = timepwt24, data=master)
```

**F**

```{r}
mainshock_f <- ivreg(formula = d_sh_empl_mfg_age1839f ~ d_impusch_p9 + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic | d_impotch_p9_lag + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic, weights = timepwt24, data=master)
```

***Summary Mainshock*** 

```{r}
stargazer(mainshock_mf, mainshock_m, mainshock_f, title = "I. Overall trade shock", dep.var.labels = c("M+F","M","F"), keep = c("d_impusch_p9"), style = "default", type = "text", dep.var.caption = "Manufacturing employment as a share of population, age 18–39", covariate.labels = "Change in Import Penetration")
```

*II. Male industry versus female industry shock*

**M+F**

```{r}
gendershock_mf <- ivreg(formula = d_sh_empl_mfg_age1839 ~ d_impuschm_p9cen + d_impuschf_p9cen + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic | d_impotchm_p9cen_lag + d_impotchf_p9cen_lag + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic, weights = timepwt24, data=master)
```

**M**

```{r}
gendershock_m <- ivreg(formula = d_sh_empl_mfg_age1839m ~ d_impuschm_p9cen + d_impuschf_p9cen + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic | d_impotchm_p9cen_lag + d_impotchf_p9cen_lag + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic, weights = timepwt24, data=master)
```

**F**

```{r}
gendershock_f <- ivreg(formula = d_sh_empl_mfg_age1839f ~ d_impuschm_p9cen + d_impuschf_p9cen + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic | d_impotchm_p9cen_lag + d_impotchf_p9cen_lag + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic, weights = timepwt24, data=master)
```

***Summary Gendershock*** 

```{r}
stargazer(gendershock_mf, gendershock_m, gendershock_f, title = "II. Male industry versus female industry shock", dep.var.labels = c("M+F","M","F"), keep = c("d_impuschm_p9cen", "d_impuschf_p9cen"), style = "default", type = "text", dep.var.caption = "Manufacturing employment as a share of population, age 18–39", covariate.labels = c("IP x Male Ind Share", "IP x Female Ind Share"))
```


*III. Male-female differential by employment status, age 18–39*

**Employed**

```{r}
mainshock_employment <- ivreg(formula = d_gender_gap_emp_1839 ~ d_impusch_p9 + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic | d_impotch_p9_lag + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic, weights = timepwt24, data=master)
```

## Earnings

Estimated Impact of Manufacturing Trade Shock on Gender Differential in Earnings, 1990-2014

**Median Earnings**

```{r}
mainshock_meanearnings <- ivreg(formula = d_gender_gap_inc1839p50 ~ d_impusch_p9 + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic | d_impotch_p9_lag + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic, weights = timepwt24, data=master)

gendershock_meanearnings <- ivreg(formula = d_gender_gap_inc1839p50 ~ d_impuschm_p9cen + d_impuschf_p9cen + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic | d_impotchm_p9cen_lag + d_impotchf_p9cen_lag + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic, weights = timepwt24, data=master)

stargazer(mainshock_meanearnings, gendershock_meanearnings, title = "Estimated Impact of Manufacturing Trade Shock on Gender Differential in Earnings, 1990-2014", dep.var.labels = c("Median Earnings","Median Earnings"), keep = c("d_impusch_p9", "d_impuschm_p9cen", "d_impuschf_p9cen"), style = "default", type = "text", dep.var.caption = "Male-female differential in annual earnings (USD), age 18–39", covariate.labels = c("Change in Import Penetration", "IP x Male Ind Share", "IP x Female Ind Share"), digits = 2)
```

## Idleness

Estimated Impact of Manufacturing Trade Shock on Gender Differential in Idleness, 1990–2014

**Employed**

```{r}
mainshock_idleness_emp <- ivreg(formula = d_gender_gap_emp_1825 ~ d_impusch_p9 + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic | d_impotch_p9_lag + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic, weights = timepwt24, data=master)

gendershock_idleness_emp <- ivreg(formula = d_gender_gap_emp_1825 ~ d_impuschm_p9cen + d_impuschf_p9cen + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic | d_impotchm_p9cen_lag + d_impotchf_p9cen_lag + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic, weights = timepwt24, data=master)
```

**Not employed, not in school**

```{r}
mainshock_idleness_noempnoschool <- ivreg(formula = d_gender_gap_noedunoemp_1825 ~ d_impusch_p9 + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic | d_impotch_p9_lag + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic, weights = timepwt24, data=master)

gendershock_idleness_noempnoschool <- ivreg(formula = d_gender_gap_noedunoemp_1825 ~ d_impuschm_p9cen + d_impuschf_p9cen + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic | d_impotchm_p9cen_lag + d_impotchf_p9cen_lag + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic, weights = timepwt24, data=master)

stargazer(mainshock_idleness_noempnoschool, gendershock_idleness_noempnoschool, title = "Estimated Impact of Manufacturing Trade Shock on Gender Differential in Idleness, 1990–2014", dep.var.labels = c("Not employed, not in school"), keep = c("d_impusch_p9", "d_impuschm_p9cen", "d_impuschf_p9cen"), style = "default", type = "text", dep.var.caption = "Male-female differential in idleness, age 18–25", covariate.labels = c("Change in Import Penetration", "IP x Male Ind Share", "IP x Female Ind Share"), digits = 2)
```

## Mortality

Estimated Impact of Manufacturing Trade Shock on Gender Differentials in Death Rates, 1990–2015

**Mortality**

```{r}
mainshock_mortality <- ivreg(formula = cum_mortmfgap_total ~ d_impusch_p9 + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic | d_impotch_p9_lag + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic, weights = timepwt24, data=master)

gendershock_mortality <- ivreg(formula = cum_mortmfgap_total ~ d_impuschm_p9cen + d_impuschf_p9cen + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic | d_impotchm_p9cen_lag + d_impotchf_p9cen_lag + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic, weights = timepwt24, data=master)

stargazer(mainshock_mortality, gendershock_mortality, title = "Estimated Impact of Manufacturing Trade Shock on Gender Differentials in Death Rates, 1990–2015", dep.var.labels = c("Total Mortality"), keep = c("d_impusch_p9", "d_impuschm_p9cen", "d_impuschf_p9cen"), style = "default", type = "text", dep.var.caption = "Male-female death rate differential ages 18–39", covariate.labels = c("Change in Import Penetration", "IP x Male Ind Share", "IP x Female Ind Share"), digits = 2)
```

## Marriage

Estimated Impact of Manufacturing Trade Shock on Marriage, 1990–2014

**Marriage**

```{r}
mainshock_marriage <- ivreg(formula = d_sh_fem1839_marrexsep ~ d_impusch_p9 + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic | d_impotch_p9_lag + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic, weights = timepwt24, data=master)

gendershock_marriage <- ivreg(formula = d_sh_fem1839_marrexsep ~ d_impuschm_p9cen + d_impuschf_p9cen + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic | d_impotchm_p9cen_lag + d_impotchf_p9cen_lag + l_shind_manuf_cbp + l_sh_popedu_c + l_sh_popfborn + l_sh_empl_f + l_sh_routine33 + l_task_outsource + t2 + reg_midatl + reg_encen + reg_wncen + reg_satl + reg_escen + reg_wscen + reg_mount + reg_pacif + l_sh_pop_black + l_sh_pop_asian + l_sh_pop_oth + l_sh_pop_hispanic, weights = timepwt24, data=master)

stargazer(mainshock_marriage, gendershock_marriage, title = "Estimated Impact of Manufacturing Trade Shock on Marriage, 1990–2014", dep.var.labels = c("Married"), keep = c("d_impusch_p9", "d_impuschm_p9cen", "d_impuschf_p9cen"), style = "default", type = "text", dep.var.caption = "Women’s marital status", covariate.labels = c("Change in Import Penetration", "IP x Male Ind Share", "IP x Female Ind Share"), digits = 2)
```


# Bartik.weight Package

We keep the structure as in the example provided for the bartik weights package (https://rdrr.io/github/jjchern/bartik.weight/f/README.md)

`bw(master, y, x, controls = NULL, weight = NULL, local, Z, global, G)`

$master$: The master data frame -> `master`  
$y$: Outcome variable. Change manufacturing employment -> `master$d_sh_empl_mfg_age1839`  
$x$: Endogenous variable. Change in import exposure -> `master$d_impusch_p9`  
$controls$: Control variables (in `master`)  
$weight$: Weighted variable. Each CZ’s share in the start-of-period population -> `timepwt24`  
$local$: The local data frame -> `bartik.weight::ADH_local` (in wide format!)  
$Z$: Local industry shares -> `bartik.weight::ADH_local$sh_ind_`  
$global$: The global data frame -> `bartik.weight::ADH_global`  
$G$: A string for the the overall industry growth rates -> `ADH_global$trade_`


```{r}
# Convert industry shares to wide format as suggested by authors in package description.
ADH_local %>%
  mutate(ind = str_glue("t{year}_sh_ind_{ind}")) %>%
  spread(ind, sh_ind_, fill = 0) %>%
  print() -> ADH_local_wide
```

Run estimation

```{r}
# Prepare variables in the master tibble
y <- "d_sh_empl_mfg_age1839" # change manufacturing employment rate
x <- "d_impusch_p9" # Growth imports from China to US
controls <- c("l_shind_manuf_cbp", "l_sh_popedu_c", "l_sh_popfborn", "l_sh_empl_f", "l_sh_routine33", "l_task_outsource", "t2", "reg_midatl", "reg_encen", "reg_wncen", "reg_satl", "reg_escen", "reg_wscen", "reg_mount", "reg_pacif", "l_sh_pop_black", "l_sh_pop_asian", "l_sh_pop_oth", "l_sh_pop_hispanic")
weight <- "timepwt24" # Weighted by population

# Prepare variables in the local tibble
# This function operates row-wise on dataframes, and element-wise among the outcomes of ps objects. The elements of setdiff(x,y) are those elements in x but not in y. The definition is taken to match the version in the base package.
Z <- setdiff(names(ADH_local_wide), c("czone", "year")) # Funktion, damit Z nur Industry share von 2000

# Prepare variables in the global tibble
G <- "trade_" # Globale Wachstumsrate: Growth imports from China to other rich countries

# Estimate the weight (alpha) and the IV estimates (beta)
bw <- bw(master, y, x, controls, weight, ADH_local_wide, Z, ADH_global, G) 
bw 

```

```{r}
# Top five Rotemberg weight industries
bw %>%
  top_n(5, alpha) %>%
  arrange(desc(alpha)) %>%
  mutate(ind = case_when(
    ind == "3571" ~ "Electronic Computers",
    ind == "3663" ~ "Radio and Television Broadcasting and Communications Equipment",
    ind == "3674" ~ "Semiconductors and Related Devices",
    ind == "3661" ~ "Telephone Apparatus",
    ind == "3679" ~ "Electronic Components, Not Elsewhere Classified"
  )) %>%
  rename(g = trade_) %>%
  knitr::kable(digits = 3, caption = "Top five Rotemberg weight industries")

# Weight of top five industries
bw %>%
  top_n(5, alpha) %>%
  transmute(sum = sum(alpha)) %>%
  slice_head(n = 1)

# Beta estimate from the bartik.weight function
bw %>% 
  mutate(b = alpha * beta) %>%
  transmute(sum = sum(b)) %>%
  slice_head(n = 1) # similar, but not identical to our previous estimate
```


sessionInfo {utils}: Collect Information About the Current R Session
```{r sessionInfo}
sessioninfo::session_info()
```

